---
title: "Group 25 Case Study"
output: pdf_document
---

Dilara Ademoğlu - 03722489  
Aynur Süne - 03725788  
Anna Illarionova - 03678137  
Samira John -  03744714  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(gridExtra)
library(gapminder)
library(dplyr)
library(data.table)
library(tidyr)
library(magrittr)
library(ggplot2)
library(magrittr) 
library(tidyverse)
library(ggrepel)
library(forcats)
library(scales)
```

```{r files}
Case <- fread('Case.csv')
PatientInfo <- fread('PatientInfo.csv')
Policy <- fread('Policy.csv')
Region <- fread('Region.csv')
SearchTrend <- fread('SearchTrend.csv')
SeoulFloating <- fread('SeoulFloating.csv')
Time <- fread('Time.csv')
TimeAge<- fread('TimeAge.csv')
TimeGender <- fread('TimeGender.csv')
TimeProvince <- fread('TimeProvince.csv')
Weather <- fread('Weather.csv')
```

### Work on Case file
```{r Case}
case_dt1 <- Case %>% select(province, confirmed) #change to df function
case_dt1 <- as.data.table(case_dt1) [, lapply(.SD, sum), 
                                     by = .(province = tolower(province))]
case_dt1 <- case_dt1[order(case_dt1$confirmed), ]
case_dt1 <- case_dt1[, proportion := confirmed / sum(confirmed) * 100]
```

# ANALYSIS ON PROVINCE

### Work on TimeProvince file
```{r TimeProvince}
timeprovince_dt <- TimeProvince %>% group_by(province)

outliers_dt <- TimeProvince[province == "Gyeongsangbuk-do" | province == "Daegu"]
outliers_dt <- outliers_dt %>% select(date, confirmed)
outliers_dt <- outliers_dt %>%
               group_by(date) %>%
               summarize(confirmed = sum(confirmed)) %>%
               ungroup

names(outliers_dt)[1:2] <- c("date", "confirmed_outliers")
time_dt <- merge(Time, outliers_dt, by = "date", all = FALSE)
time_dt <- time_dt[, no_outliers := confirmed - confirmed_outliers]

```

## Plot Nr.1: Population* in provinces 
(*Data is obtained from __[here](http://index.go.kr/potal/main/EachDtlPageDetail.do?idx_cd=1007#quick_01)__)
```{r plot1, echo=TRUE}
case_dt1 <- case_dt1[order(case_dt1$province), ] #sort in alph. order
case_dt1 <- case_dt1[, population := as.integer(c("3373","1626","2188","2432","1509",
                                                  "1517","1494","13238","2665","3350",
                                                  "2944","660","1803","1773","331",
                                                  "9662","1147"))]

case_dt1 <- case_dt1[order(case_dt1$population), ]

plot1 <- ggplot(case_dt1, aes(x = reorder(province, population), y = population)) +
         geom_bar(stat = "identity",
                  color = "black",
                  fill = "mediumpurple",
                  alpha = 0.7) +
         coord_flip() +
         geom_text(aes(label = population, y = population + 500), size = 3) +
         labs(x = 'Province', y = 'Population') +
         ggtitle("Province population") +
         theme_bw()

plot1
```

## Plot Nr.2: Cases in provinces
```{r plot2, echo=TRUE}
plot2 <- ggplot(case_dt1, aes(x=reorder(province, confirmed),y=confirmed)) +
         geom_bar(stat="identity",color="black",fill= "orchid", alpha = 0.7) +
         coord_flip() +
         geom_text(aes(label=confirmed, y = confirmed+250), size=3) +
         labs(x='Province', y='Total Number of Confirmed Cases') +
         ggtitle("Cases in provinces over time") +
         theme_bw()

plot2
```

## Plot Nr.3: Comparison of population and number of cases
```{r plot3}
require(gridExtra)
grid.arrange(plot1, plot2, ncol=2)
```

## Plot Nr.4: Proportion of total cases by province
```{r plot4, echo=TRUE}
case_dt1 <- case_dt1[order(case_dt1$proportion),]
case_dt1$province <- factor(case_dt1$province, 
                            levels = rev(as.character(case_dt1$province)))
case_dt1_x <- case_dt1 %>%
              arrange(desc(province)) %>%
              mutate(y = proportion / sum(proportion), y.stack = cumsum(y)) %>%
              ungroup()

ggplot(case_dt1_x, aes(x='', label=paste0(round(proportion), "%"), y=y, fill=province))+
  geom_bar(stat="identity", width=1, color="black") +
  coord_polar("y") +
  geom_text(aes(label=paste0(round(proportion),"%")),position=position_stack(vjust=0.5))+
  ggtitle("Cases proportion by provinces")+
  scale_fill_manual(values = rev(c("#ededed", "#f2e6e2", "#f6dfd8", "#fbd8cd","#ffd1c2",
                                   "#f7cac9", "#dec2cb", "#c5b9cd", "#abb1cf","#92a8d1",
                                   "#7483c9","#8b74d4","#a166df","#b857ea","#ce48f5",
                                   "#800490","#70038c"))) +
  theme_void()
```

## Plot Nr.5: Cases in provinces without 2 outliers
```{r plot5, echo=TRUE}
case_dt2<-case_dt1[!(case_dt1$province=="daegu" | case_dt1$province=="gyeongsangbuk-do"),]
plot5<-ggplot (case_dt2, aes(x=reorder(province, confirmed),y=confirmed))+
  geom_bar(stat="identity", color="black",fill= "orchid", alpha = 0.7)+
  coord_flip()+
  geom_text(aes(label=confirmed), hjust= - 0.1, size=2.5)+
  labs( x='Province', y='Total Number of Confirmed Cases') +
  ggtitle("Cases in provinces over time (without outliers)")+
  theme_bw()

plot5
```

## Plot Nr.6: Population in provinces without 2 outliers
```{r plot6, echo=TRUE}
case_dt1 <- case_dt1[order(case_dt1$province),] #sort in alph. order
case_dt1 <- case_dt1[, population:= as.integer(c("3373","1626","2188",
                                                 "2432","1509","1517",
                                                 "1494","13238","2665",
                                                 "3350","2944","660",
                                                 "1803","1773","331",
                                                 "9662","1147"))]

plot6 <- ggplot (case_dt2, aes(x=reorder(province, population), y=population))+
  geom_bar(stat="identity", color="black",fill= "mediumpurple", alpha = 0.7)+
  coord_flip()+
  geom_text(aes(label=population), hjust=-0.05, size=2.2)+
  labs( x='Province', y='Population') +
  ggtitle("Province population (without outliers)")+
  theme_bw()

plot6
```

## Plot Nr.7: Comparison of Plot Nr.1 and Plot Nr.4
```{r plot7, echo=TRUE}
require(gridExtra)
grid.arrange(plot5, plot6, ncol=2)
```

## Plot Nr.8: General overview
```{r plot8, echo=TRUE}
colors <- c("total confirmed" = "mediumpurple4", 
            "outliers" = "mediumorchid3", 
            "without outliers" = "plum2")

ggplot(time_dt, aes(x=date)) + 
  geom_line(aes(y=confirmed, color="total confirmed")) + 
  geom_point(aes(y=confirmed, color="total confirmed")) +
  geom_line(aes(y=confirmed_outliers, color="outliers")) + 
  geom_point(aes(y=confirmed_outliers, color="outliers")) +
  geom_line(aes(y=no_outliers, color="without outliers")) + 
  geom_point(aes(y=no_outliers, color="without outliers"))+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  labs(x='Date', y='Number of total confirmed cases', color="Legend") +
  ggtitle("Cases in provinces over time")+
  scale_color_manual(values = colors)+
  theme_bw()
```

# ANALYSIS ON GENDER AND AGE

## Plot Nr.9: Accumulated confirmed cases by age group
```{r}
TimeAge[, date := as.Date(date, "%Y-%m-%d")]
ggplot(TimeAge, aes(
  x = date,
  y = confirmed,
  color = age,
  group = age
)) +
  geom_line() + geom_point() +
  ggtitle("Accumulated confirmed cases by age group") +
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  labs(x = "Time", y = "Accumulated confirmed cases") + theme_bw()
```

```{r}
TimeGender[, date := as.Date(date, "%Y-%m-%d")]
gender_reshape <- melt(TimeGender,
                       id.vars = c("date", "sex", "time"),
                       measure.vars = c("confirmed", "deceased"))
female_time <- gender_reshape[sex == "female"]
male_time <- gender_reshape[sex == "male"]
```

## Plot Nr.10: Accumulated confirmed and deceased cases over time
```{r}
ggplot(gender_reshape, aes(x = date, y = value, col = variable)) + 
  geom_point() +
  labs(x = "Time", y = "Number of cases", 
       title = "Accumulated confirmed and deceased cases over time",
       subtitle = "male and female") +
  scale_color_manual("sex", values = c("deceased" = "coral2", 
                                       "confirmed" = "deepskyblue3")) +
  facet_wrap( ~ sex) + 
  theme_bw()
```

## Plot Nr.11: Accumulated confirmed and deceased cases over time
### By gender
```{r}
ggplot(gender_reshape, aes(x = date, y = value, col = variable)) + geom_point() +
  labs(
    x = "Time",
    y = "Number of cases",
    title = "Accumulated confirmed and deceased cases over time",
    subtitle = "By Gender"
  ) +
  scale_color_manual("sex",
                     values = c("deceased" = "coral2", "confirmed" = "deepskyblue3")) +
  facet_wrap(~ sex) + theme_bw()
```

## Plot Nr.12: Accumulated number of cases over time 
### By state of patients
```{r}
# reshape time data
time_reshape <- melt(Time,
                     id.vars = "date",
                     measure.vars = c("confirmed", "released", "deceased"))

ggplot(time_reshape, aes(x = date, y = value, col = variable)) +
  geom_point() + geom_line() +
  labs(x = "Time",
       y = "Number of cases",
       title = "Accumulated number of cases over time",
       subtitle = "By state of patients") +
  scale_color_manual("state",
                     values = c("deceased" = "coral2",
                                "confirmed" = "deeppink",
                                "released" = "palegreen3")) +
  theme_bw()
```

### Working on PatientInfo 
```{r}
PatientInfo[sex == "female", .N]
PatientInfo[sex == "male", .N]
PatientInfo$age <- factor(PatientInfo$age,
                          levels = c("0s","10s","20s","30s",
                                     "40s","50s","60s","70s",
                                     "80s", "90s","100s"))

patient_state_sex <- PatientInfo[sex != "", .(sex, age, confirmed_date, state)]
patient_state_sex[, state := as.factor(state)]
patient_state_sex[, sex := as.factor(sex)]
sapply(patient_state_sex, class)
dead_patients_bysex <- patient_state_sex[state == "deceased"]
```

## Plot Nr.13: Confirmed case distribution by state
### Gender vs Age
```{r}
patient_state_sex %>%
  filter(is.na(confirmed_date) == F) %>%
  filter(is.na(age) == F) %>%
  ggplot(., aes(x = sex, y = age, col = state)) +
  geom_jitter() +
  labs(
    title = "Confirmed case distribution by state",
    subtitle = "Gender vs Age",
    y = "Age",
    x = "Gender"
  ) + facet_wrap( ~ state) +
  scale_color_manual(
    "state",
    values = c(
      "deceased" = "coral2",
      "isolated" = "darkorchid1",
      "released" = "palegreen3"
    )
  ) +
  theme_bw()
```

## Plot Nr.14: Deceased cases by age
### Categorized by gender
```{r}
dead_patients_bysex %>%
  group_by(sex, age) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = age, y = count, fill = sex)) + geom_bar(stat = "identity") +
  geom_text(aes(label = count, y = count + 1), size = 4.5) +
  labs(
    x = "Age",
    y = "Number of cases",
    title = "Deceased cases by age",
    subtitle = "Categorized by gender"
  ) +
  scale_fill_manual("sex",
                    values = c("female" = "indianred1", "male" = "cornflowerblue")) +
  facet_wrap( ~ sex) + coord_flip() + theme_bw()
  
```

## Plot Nr.15: Cases by age
### Categorized by gender
```{r}
patient_state_sex %>%
  filter(is.na(confirmed_date) == F) %>%
  filter(is.na(age) == F) %>%
  group_by(sex, age, state) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = age, y = count, fill = state)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(
    x = "Age",
    y = "Number of cases",
    title = "Cases by age",
    subtitle = "Categorized by gender"
  ) +
  scale_fill_manual(
    "state",
    values = c(
      "deceased" = "coral2",
      "isolated" = "darkorchid1",
      "released" = "palegreen3"
    )
  )  +
  facet_wrap( ~ sex) + theme_bw() 

```

## Plot Nr.16: Case ratios by age
```{r}
patient_state_sex %>%
  filter(is.na(confirmed_date) == F) %>%
  filter(is.na(age) == F) %>%
  group_by(sex, age, state) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = age, y = count, fill = state)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(x = "Age", y = "Percentage of cases", title = "Case ratios by age") +
  scale_fill_manual(
    "state",
    values = c(
      "deceased" = "coral2",
      "isolated" = "darkorchid1",
      "released" = "palegreen3"
    )
  )  + coord_flip() + theme_bw()
```

## Plot Nr.17: Case ratios by age
### By gender
```{r}
patient_state_sex %>%
  filter(is.na(confirmed_date) == F) %>%
  filter(is.na(age) == F) %>%
  group_by(sex, age, state) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = age, y = count, fill = state)) + 
    geom_bar(stat = "identity", position = "fill") +
    labs(x = "Age",
         y = "Percentage of cases",
         title = "Case ratios by age",
         subtitle = "By gender") +
    scale_fill_manual("state", values = c("deceased" = "coral2",
                                          "isolated" = "darkorchid1",
                                          "released" = "palegreen3")) +
    facet_wrap( ~ sex) + 
    coord_flip() + 
  theme_bw()
```

## Plot Nr.18: Case ratios by gender
```{r}
patient_state_sex %>%
  filter(is.na(confirmed_date) == F) %>%
  filter(is.na(age) == F) %>%
  group_by(sex, age, state) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = sex, y = count, fill = state)) + 
  geom_bar(stat = "identity", position = "fill") +
  labs(x = "Gender", y = "Percentage of cases", title = "Case ratios by gender") +
  scale_fill_manual("state", values = c("deceased" = "coral2",
                                        "isolated" = "darkorchid1",
                                        "released" = "palegreen3")) +
   coord_flip() +  
   theme_bw() 
```

## Plot Nr.19: Number of cases by gender groups
### Categorized by state of patients
```{r}
patient_state_sex %>%
  group_by(sex, state) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = sex, y = count, fill = state)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = scales::percent(round((count) / sum(count), 3)), 
                y = count + 60), size = 4) +
  geom_text(aes(label = count, y = count + 140), size = 4) +
  labs(x = "Gender", y = "Number of cases",
       title = "Number of cases by gender groups",
       subtitle = "Categorized by state of patients") +
  facet_wrap( ~ state) +
  scale_fill_manual("state", values = c("deceased" = "coral2",
                                        "isolated" = "darkorchid1",
                                        "released" = "palegreen3")) +
  theme_bw()

```

## Plot Nr.20: Case ratios by state
### By gender
```{r}
patient_state_sex %>%
  filter(is.na(confirmed_date) == F) %>%
  group_by(sex, state) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = state, y = count, fill = sex)) + 
  geom_bar(stat = "identity", position = "fill") +
  labs(x = "State of patients", y = "Percentage of cases",
       title = "Case ratios by state",
       subtitle = "By gender") +
  scale_fill_manual("sex", values = c("female" = "indianred1", 
                                      "male" = "cornflowerblue")) +
  coord_flip() + 
  theme_bw()
```

## Plot Nr.21: Case ratios by sge
### By gender
```{r}
patient_state_sex %>%
  filter(is.na(confirmed_date) == F) %>%
  filter(is.na(age) == F) %>%
  group_by(sex, state, age) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = age, y = count, fill = sex)) + 
  geom_bar(stat = "identity", position = "fill") +
  labs(x = "Age", y = "Percentage of cases",
       title = "Case ratios by age",
       subtitle = "By gender") +
  scale_fill_manual("sex", values = c("female" = "indianred1", 
                                      "male" = "cornflowerblue")) +
  coord_flip() + 
  theme_bw()
```

## Plot Nr.21: Number of cases by gender ratios
### Deceased
```{r}
dead_patients_bysex %>%
  group_by(sex) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = sex, y = count, fill = sex)) +
  geom_bar(stat = "identity") +
  labs(x = "Gender", y = "Number of deceased cases",
       title = "Number of cases by gender ratios",
       subtitle = "Deceased") +
  geom_text(aes(label = scales::percent(round((count) / sum(count), 3)),
                y = count + 5), size = 4.5) +
  geom_text(aes(label = count, y = count + 10), size = 4.5) +
  coord_flip() +
  scale_fill_manual("sex", values = c("female" = "indianred1", 
                                      "male" = "cornflowerblue")) +
  theme_bw()
```

## Plot Nr.22: Number of cases by gender ratios
### Released and isolated
```{r}
patient_state_sex %>%
  filter(state != "deceased") %>%
  group_by(sex) %>%
  summarise(count = n()) %>%
  ggplot(., aes(x = sex, y = count, fill = sex)) +
  geom_bar(stat = "identity") +
  labs(x = "Gender", y = "Number of released cases",
       title = "Number of cases by gender ratios",
       subtitle = "Released and isolated") +
  geom_text(aes(label = scales::percent(round((count) / sum(count), 3)), 
                y = count + 80), size = 4.5) +
  geom_text(aes(label = count, y = count + 350), size = 4.5) +
  coord_flip() +
  scale_fill_manual("sex", values = c("female" = "indianred1", 
                                      "male" = "cornflowerblue")) +
  theme_bw()
```

# ANALYSIS ON GOVERNMENT POLICIES

```{r work on time_data file, echo=TRUE}
#value for zero row
Time[, confirmed_per_day := confirmed - shift(confirmed, fill = 0, type = 'lag')] 
```

## Plot Nr.23: Accumulated number of confirmed cases over given time period
### (2020-01-20 to 2020-06-30)
```{r plot accumulated cases}
plot_1 <- ggplot(Time, aes(date, confirmed)) + 
  geom_point(size = 1) + 
  geom_line(size = 0.25) +
  scale_color_brewer(palette='Set3') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'Number of confirmed cases',
       title = 'Accumulated number of confirmed cases over given time period',
       subtitle = '(2020-01-20 to 2020-06-30)') +
  theme_bw()

plot_1
```

## Plot Nr.24: Number of confirmed cases per day over given time period
### (2020-01-20 to 2020-06-30)
```{r plot cases per day}
plot_2 <- ggplot(Time, aes(date, confirmed_per_day)) + 
  geom_point(size = 1) + 
  geom_line(size = 0.25) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'Number of confirmed cases',
       title = 'Number of confirmed cases per day over given time period',
       subtitle = '(2020-01-20 to 2020-06-30)') +
  theme_bw()

plot_2
```

### Working on Policy

Rearranging and merging data
```{r policy, echo=TRUE}
policy_reshaped <- Policy[, date := start_date] #variable date to identify observations
policy_merged <- merge(Time, policy_reshaped, by='date', group_by='date',all=TRUE) %>%
                 as.data.table(policy_merged)

policy_sum <- Policy[, .(count = .N), by=date] 
policy_sum[, count_accumulated := cumsum(count)]
```

```{r correlation}
policy_sum <- merge(policy_sum, Time, by='date', group_by='date', all=TRUE)
```

## Plot Nr.25: Comparison of Accumulated Confirmed Cases and  
Accumulated Number of Government Policy
### (2020-01-20 to 2020-06-30)
```{r development number of cases - number policies}
plot1.1 <- ggplot(policy_sum, aes(date, confirmed)) + 
           geom_point() + 
           labs(x = 'Date', y = 'Accumulated Number of Confirmed Cases') +
           theme_bw()

plot3.1 <- ggplot(policy_sum, aes(date, count_accumulated)) + 
           geom_point() + 
           labs(x = 'Date', y = 'Accumulated Number of Government Policy') +
           theme_bw()

grid.arrange(plot1.1, plot3.1, ncol=2)
```

## Plot Nr.26: Show events of government policies
```{r}
ggplot(policy_merged, aes(date, confirmed)) + 
  geom_line() + 
  geom_point(size=2) +
  geom_vline(aes(xintercept = date, color = type), size = 0.25, linetype = 'dashed') + 
  labs(color = 'Government policy type') +
  scale_color_brewer(palette='Set1') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'Number of confirmed cases',
       title = "Accumulated Number of Confirmed Cases",
       subtitle = "With start date of government policies") +
  theme_bw()
```


## Plot Nr.27: Show events of government policies
```{r plot policies, echo=TRUE}
plot_3 <- ggplot(policy_merged, aes(date, confirmed_per_day)) + 
          geom_line() + 
          geom_vline(aes(xintercept=date, color=type), size=0.3, linetype = 'dashed') + 
          labs(color = 'Government policy type') +
          scale_color_brewer(palette='Set1') +
          theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
          labs(x = 'Date', y = 'Number of confirmed cases',
               title = "Number of Confirmed Cases per day",
               subtitle = "With start date of government policies") +
          theme_bw()

plot_3
```

## Plot Nr.28: Show events of government policies
### For the first big peak
```{r plot policies - compressed time period, fig.show=TRUE}
policy_merged_reshaped1 <- policy_merged[date >= as.Date("2020-01-03") & 
                                         date <= as.Date("2020-04-15"),
                                         .(date,confirmed_per_day,
                                           type,detail,start_date)]
#for a better overview of the data
ggplot(policy_merged_reshaped1, aes(date, confirmed_per_day)) + 
  geom_line() + 
  geom_vline(aes(xintercept = date, color = type), size = 0.3, linetype = 'dashed') +
  labs(color = 'Government policy type') +
  scale_color_brewer(palette='Set1') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'Number of confirmed cases',
       title = "Number of Confirmed Cases per day",
       subtitle = "With start date of government policies") +
  theme_bw()
```

## Plot Nr.29: Alert Level of Policies
```{r alert level}
alert_level <- Policy[type == 'Alert']
alert_level[,date] #View start_date of each Alert Level

plot_4 <- ggplot(policy_merged, aes(date, confirmed_per_day)) + 
  #Geom_rect for Level 1
          geom_rect(aes(xmin = as.Date("2020-01-03", "%Y-%m-%d"), 
                        xmax = as.Date("2020-01-19",  "%Y-%m-%d"), 
                        ymin = -Inf, ymax = Inf, fill = 'Alert Level 1'), 
                    alpha = 0.03) +
          #Geom_rect for Level 2
          geom_rect(aes(xmin = as.Date("2020-01-20", "%Y-%m-%d"), 
                        xmax = as.Date("2020-01-27",  "%Y-%m-%d"), 
                        ymin = -Inf, ymax = Inf, fill = 'Alert Level 2'), 
                    alpha = 0.03) + 
          #Geom_rect for Level 3
          geom_rect(aes(xmin = as.Date("2020-01-28", "%Y-%m-%d"), 
                        xmax = as.Date("2020-02-22",  "%Y-%m-%d"), 
                        ymin = -Inf, ymax = Inf, fill = 'Alert Level 3'), 
                    alpha = 0.03) +
          #Geom_rect for Level 4
          geom_rect(aes(xmin = as.Date("2020-02-23", "%Y-%m-%d"), 
                        xmax = as.Date("2020-06-30",  "%Y-%m-%d"), 
                        ymin = -Inf, ymax = Inf, fill = 'Alert Level 4'), 
                    alpha = 0.03) +
          geom_line() +
          scale_fill_manual(name ='',
                            values = c('lightblue','yellow', 'orange','red'),  
                            guide = guide_legend(override.aes = list(alpha = 1))) +
          theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
          labs(x = 'Date', y = 'Number of confirmed cases') +
          ggtitle('Alert levels')+ theme_bw()

plot_4
```

## Plot Nr.30: Policies on Administration
```{r administration}
Policy[type=='Administrative', 4:6] # view all policy titles on administration

ggplot(policy_merged, aes(date, confirmed_per_day)) + 
  geom_line() + 
  geom_vline(data = subset(policy_merged, type == 'Administrative'), # filter data source
             aes(xintercept = start_date, 
                 color = c('close bars and clubs',
                           'local government administrative orders',
                           'close karaoke')), size = 0.3, linetype = 'dashed') + 
  labs(color = 'Government policy') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'Number of confirmed cases') +
  ggtitle('Policies on Administration') + 
  theme_bw()
```

## Plot Nr.31: Policies on Education
```{r education}
Policy[type=='Education', 4:6] %>% 
  group_by(start_date) #view all policy titles on education
#summarize policy titles for each start_date
policy_education <- Policy[type=='Education', .(date=unique(start_date))] 
policy_education[,gov_policy_grouped := c('school closure & opening delay',
                                          'online class open (high&middle 3)',
                                          'online class open (high&middle 
                                          1,2/elementary 4-6)',
                                          'online class open (elementary 1-4)')] 

ggplot(policy_merged, aes(date, confirmed_per_day)) + 
  geom_line() + 
  geom_vline(data = subset(policy_education, date==date), # filter data source
             aes(xintercept = date, 
                 color=c('school closure & opening delay',
                         'online class open (high&middle 3)',
                         'online class open (high&middle 1,2/elementary 4-6)',
                         'online class open (elementary 1-4)')), size = 0.3, 
             linetype = 'dashed') + 
  labs(color = 'Government policy') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'Number of confirmed cases') +
  ggtitle('Policies on Education') + 
  theme_bw()
```

## Plot Nr.32: Policies on Public Health
```{r health}
Policy[type=='Health', 4:6] %>% group_by(start_date) #view all policy titles on health
policy_health <- Policy[type=='Health',.(start_date=first(start_date)), 
                        by=gov_policy] #only first policy implementation

ggplot(policy_merged, aes(date, confirmed_per_day)) + 
  geom_line() + 
  geom_vline(data = policy_health, 
             aes(xintercept = start_date,
                 color = c('emergency use authorization of diagnostic kit',
                           'drive-through screening center', 'mask distribution',
                           'extends tightened quarantine measures' )), size = 0.3, 
             linetype = 'dashed') + 
  labs(color = 'Government policy') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'Number of confirmed cases') +
  ggtitle('Policies on Public Health') + 
  theme_bw()
```

## Plot Nr.33: Policies on Immigration
```{r immigration}
Policy[type=='Immigration', 4:6] %>% 
  group_by(start_date) #view all policy titles on health

policy_immigration <- Policy[detail=='from China'|detail=='from all the countries'|
                               detail=='from U.S.',4:6] #select representative policies

ggplot(policy_merged, aes(date, confirmed_per_day)) + 
  geom_line() + 
  geom_vline(data = policy_immigration, 
             aes(xintercept = start_date, color = c('blue','red','yellow','green')), 
             size = 0.3, linetype = 'dashed') + 
  scale_color_identity(name='', 
                       breaks=c('blue','red','yellow','green'),
                       labels=c('special immigration procedure (China)',
                                'special immigration procedure (all countries)',
                                'mandatory 14-day self-quarantine (all countries)',
                                'mandatory self-quarantine & diagnostic tests (U.S.)'),
                       guide = 'legend') + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'Number of confirmed cases') +
  ggtitle('Policies on Immigration') + 
  theme_bw()
```

## Time of Execution
```{r time of execution}
policy_merged_reshaped <- policy_merged[date >= as.Date("2020-02-23") &
                                        date <= as.Date("2020-06-30"),
                                        .(date,confirmed_per_day,type,detail,start_date)] 
#for a better overview of the data

time_slope <- policy_merged_reshaped %>% 
              mutate(slope = confirmed_per_day - shift(confirmed_per_day, 
                                                       fill = 0, type = 'lag')) 
```

## Plot Nr.34: Slope of the case numbers and policy start date intersections
```{r time of execution 2}
plot_5 <- ggplot(time_slope, aes(x=date, y=slope)) + 
  geom_vline(data = subset(Policy, start_date == date), # filter data source
             aes(xintercept = date, color = type), 
             size = 0.3, linetype = 'dashed') +
  geom_line(aes(x=date, y=slope)) +
  labs(color = 'Government policy type') +
  geom_point(data = subset(time_slope, start_date == date & slope>0), 
             aes(x=date, y=slope, color=type )) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
  labs(x = 'Date', y = 'slope', 
       subtitle='Positive slope and policy start date intersection') +
  ggtitle('Introduced government policy when number of confirmed cases is rising') + 
  theme_bw()

plot_5
```

## Plot Nr.35: Comparison of Number of Confirmed Cases and Slope with policy dates
```{r plot comparison}
require(gridExtra)
grid.arrange(plot_3, plot_5, nrow=2)
```

